Figure 2a

### 2017-11-17 inst/figure2a_HCT116p53null/figure2a_HCT116p53null.Rmd
added gatherFigures and clearFigures functions and ran

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2a_stableLineExpressionHEK/suppFigure2a_stableLineExpressionHEK.pdf"

#ggsave(
#  plot = figure, 
#  filename = path, 
#  device = cairo_pdf, 
#  height = 60,
#  width = 83,
#  units = "mm"
#)
```

>>>>

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/figure2a_HCT116p53null/figure2a_HCT116p53null.pdf"

ggsave(
 plot = figure,
 filename = path,
 device = cairo_pdf,
 height = 60,
 width = 83,
 units = "mm"
)
```
